---
title: "Dark Web Market"
author: "Simon Delecourt & Edouard Donze"
output:
  html_notebook:
    code_folding: hide
    highlight: pygments
    number_sections: yes
    theme: readable
    toc: yes
    toc_float: yes
bibliography: My_bibliography.bibtex
---
<style>
body {text-align: justify}
</style>

# - Introduction
***
For the past few years, a lot of *web market* has been developed and you can now find or buy items of any kind. However plenty of those marketplace are growing up on the *dark web*. Even if the government attempt to fight against this kind of illegal market, new one resurface or re-migrate frequently. On top of that, currently, we don't know enough of how these websites
operate
<br/>  
This paper present a research carried out on one of the larger marketplace (specially for drugs) on the Internet, the ***AlphaBay Dark Web Market***.  
Our work consist in analysing this market, its nature, preponderance of items, different country of origin, main sellers ... Thus, over a first phase wee have performed some "Basic Statistics" on the *Data*, in order to discover the marketplace and to point out its trend. Then in section 3, wee present some experimental results of *data mining* and discuss on it.


```{r Library, message=FALSE, warning=FALSE}
#----------------------------------------------------------
#                       Library :
#----------------------------------------------------------

#install.packages("stringr")
#install.packages("units")
#install.packages("ggmap")
#install.packages("plotrix")
#install.packages("rattle")
#install.packages("rpart")
#install.packages("rpart.plot")
#install.packages("RColorBrewer")
#install.packages("arules")
#install.packages("arulesViz")
#install.packages("e1071")

# Mamipulation string
library(stringr)

# Using unit
library(units)

# Plot a map
library(ggmap)
library(plotrix)

# Decision Tree
library(rattle)
library(rpart)
library(rpart.plot)
library(RColorBrewer)

# Association rules
library(arules)
library(arulesViz)

# Bayesian classification, naive algorithm
library(e1071)

```

```{r Importation}
#----------------------------------------------------------
#               Importation of the data :
#----------------------------------------------------------

data <- as.data.frame(read.csv("../alphaClean.csv"))
```

RMarkdown [@baumer2014r] is referenced in the @racine2012rstudio paper.  
@WinNT

# - Basic Statistics
***
We have perform basics statics in order to discover the data. 

1. First of all, here is a general view of ads distribution in the world.

```{r Number of ads}
#-----------------------------------------------
#      Number of ads in the world
#-----------------------------------------------

NumberOfAds <- function() {

  # Get rid of unwanted orign like Worldwide and Null which are not relevant
  matching_vector <- c(  !str_detect(data$origin, "Worldwide") & !str_detect(data$origin, "NULL"))
  
  sumup <- sort(summary(data[matching_vector, "origin"]), decreasing=TRUE)
  
  # Bar plot with the total number ofs ads in each country
  
  par(las=1)#display yaxis horizontally
  par(mar=c(6,8,4,3)) #give space for yaxis
  
  barp <- barplot(sumup[1:10], main="Number of ads in the World", xlim= c(0,max(sumup[1:10])+500), xlab="Number of ads",horiz = TRUE,  col = rainbow(10), cex.names = 0.8)
  
  # Ad numbers at the end of each bar
  barp <- text(y = barp, x = sumup[1:10], label = sumup[1:10], pos=4 , cex = 0.8, col= "black")
  
  # Frame
  box(which = "outer", lty = "solid")

}
  
NumberOfAds()

```
The bar-chart represents the 10 main dealers in the world regarding the number of ads. As we can see, US is the biggest dealer far ahead of other. Their number of ads is more than twice as big as the number of the second (UK). Moreover, most of these countries are developed countries, that is to say US and European countries. We can also notice that China and Afghanistan are presents.  

2. Now let's see the distribution of ads per category.

```{r Function Select Drugs}
  selectDrug <- function(drugName){
    matching_vector <- c( (str_detect(data$category, drugName)))
    return(matching_vector)
  }
```


```{r}

categ <- function(){
  
  cat <- c()
  
  for(i in 1:length(data$category)) {
    cat[i] <- unlist(strsplit(as.character(data$category[i]), "/"))[2]
    if(is.na(cat[i])) {cat[i] <- "Other Listings"}
  }
  
  tab_cat <- table(cat)
  #tab_cat <- sort(tab_cat, deacrising=TRUE)
  
  radial.pie(tab_cat,labels=names(tab_cat),mar=c(3,0,3,0))
}

categ()

```

```{r}
RateDrugAd <- function() {

  rate <- c()
  
  NbAd <- nrow(data)
  
  # Select all "Drugs & Chemicals" ads
  matching_vector <- c( str_detect(data$category, "Drugs & Chemicals"))
  drug.data <- data[matching_vector,]
  
  NbAdDrug <- nrow(drug.data)
  
  rate[1] <- round((NbAdDrug/NbAd)*100,2)
  
  # Select all "Frau" ads
  matching_vector <- c( str_detect(data$category, "Fraud"))
  fraud.data <- data[matching_vector,]
  
  NbAdFraud <- nrow(fraud.data)
  
  rate[2] <- round((NbAdFraud/NbAd)*100,2)
  
  return(rate)
}

rate <- RateDrugAd()

```

et la si j'affiche `r rate[1]` % est ce que ca marche `r rate[2]` %


```{r Distribution of Drugs}
#-----------------------------------------------
#      Distribution of Drugs in the market
#-----------------------------------------------

DistributionDrugs <- function() {

  #----------------------------
  #   The most common drugs
  #----------------------------
  
  drugs <- c("Cocaine", "Meth", "LSD", "Opioids", "Cannabis", "Steroids", "Ecstasy", "Ketamine", "Heroin", "Shrooms", "Tobacco", "Benzos", "Paraphernalia")
  
  freq <- c()
  for(i in 1:length(drugs)){
    matching_vector <- selectDrug(drugName=drugs[i]);
    sumup<-summary(matching_vector)
    freq[i] <- sumup[3]
  }
  
  freq <- as.numeric(freq)
  res <- data.frame(drugs, freq)
  res <- res[order(res$freq, decreasing = TRUE),]
  
  #----------------------
  #     Pie Chart 
  #----------------------
  
  # 1- Labels :
  # Calculation in percentage
  piepercent<- round(100*res$freq/sum(res$freq), 1)
    # round(a,1) : one digit after the comma
  
  lab <- c()
  
  for(i in 1:length(piepercent)) {
    lab[i] <- paste(piepercent[[i]], "%", sep=" ")
  }
  
  # 2- Title :
  title <- "Distribution of drugs"
  
  # 3- Colors :
  c <- rainbow(length(piepercent))
  
  # 4- Plot :
  pie3D(piepercent,labels = lab,labelcex = 1, main = title ,col=c, theta = 0.9, explode = 0.04)
  
  # 5- Legend :
  legend(x=-2.5,y=-1.1,res$drugs, cex = 0.9, fill = c,ncol=5,border=NA, xpd=NA)
  
  # Frame
  box(which = "inner", lty = "solid")
}

DistributionDrugs()

```

At first sight, drugs and chemicals are principle products dealt in the black market. They represents more than 50% of the global market. It is also interesting to see that the second product that is sold is counterfeit and paper fraud. On top of that, we can notice that a small percentage concern Jewel, Gold and Weapon.  


3. Let's focus on Drugs Market now.

```{r Number of ads of Drugs}
#---------------------------------------------
#    Number of ads of Drugs in the world
#---------------------------------------------

NumberOfAdsDrugs <- function(){

  # Get rid of unwanted orign like Worldwide and Null which are not relevant
  matching_vector <- c( str_detect(data$category, "Drugs") & !str_detect(data$origin, "Worldwide") & !str_detect(data$origin, "NULL"))
  
  sumup <- sort(summary(data[matching_vector, "origin"]), decreasing=TRUE)
  
  # Bar plot with the total number of ads of Drugs in each country
  par(las=1)#display yaxis horizontally
  par(mar=c(6,8,3,3)) #give space for yaxis
    
  barp <- barplot(sumup[1:10], main="Number of ads of Drugs in the World", xlab="Number of ads",xlim = c(0,max(sumup[1:10]+500)),  col = rainbow(10), cex.names = 0.8, horiz = TRUE)
  barp <- text(y = barp, x = sumup[1:10], label = sumup[1:10], pos=4 , cex = 0.8, col= "black")
  
  # Frame
  box(which = "outer", lty = "solid")

}

NumberOfAdsDrugs()

```


At first sight, the chart is similar to the first one. This is coherent, indeed by comparing the ratio between drugs ads and the total number of ads, we can deduced that there are mainly dealing drugs. This also match with the second chart that show us that drugs are the main product in the market. There are few exceptions such as Afghanistan which has been replaced by India and Canada has been reversed with China. Finally, let's note that drugs market is gathered in Europe and United States.


4. Take a global view of the drugs market in Europe with the following map.

```{r Europe Map, message=FALSE}

MapEurope <- function() {

  # Select the ads about drugs and get rid of the irrelevant orign Worlwide
  matching_vector <- c( (str_detect(data$category, "Drugs") ) & !str_detect(data$origin, "Worldwide"))
  
  sumup <- sort(summary(data[matching_vector, "origin"]), decreasing=TRUE)
  
  # Read a file containing the latitude and longitude of the "center" of each country
  data_country <- read.csv("./Stats/lat_long.csv")
  lat_long <- data.frame(Country = data_country$Country , long=  data_country$Longitude..average., lat=  data_country$Latitude..average.)
  
  # Create a data.frame with the name of the country and its nb of ads
  v <- data.frame(name= names(sumup) , amount = sumup)
  
  # Merge v with lat_long in order to have a data with Country/NbofAds/lattitude/longitude
  data_plot <- merge(v, lat_long,  by.x = "name", by.y = "Country" )
  
  # Create a map of EUROPE with circles showing the amount of ads
  map <- get_map(location = 'Europe', zoom =4 )
  mapPoints <- ggmap(map)  + xlab("") + ylab("") + ggtitle("Number of ads of Drugs in the World")+
    geom_point(data = data_plot,aes(x =long, y = lat, size =amount)) +scale_size_continuous(limits=c(0,3000),breaks=c(0,500,1000,1500,2000), range = c(0,13)) 
  
  # Display
  mapPoints

}

MapEurope()

```

Circles shows the amount of ads about drugs. The map confirms our assumptions that there are a lot of Drug dealers in Europe with, as major dealers countries, United Kingdom, Netherlands and Germany.  


5. The pie chart below represents the repartition of each categories that United Kingdom exports. We focused on the second subcategory which appears to be most the relevant since the first one is too wide and the third one is often "Other".



```{r Exportation UK}
#-----------------------------------------------
#   Importation / Exportation of a country
#-----------------------------------------------

country_Export <- function() {

  #-------------------
  #  Initialization
  #-------------------

  country <- "United Kingdom"
  num <- 0
  
  # Importation / Exportation :
  if (num == 0) { 
    way <- "origin"
    txt <- "- Exportation"
  } else if (num == 1) {
    way <- "destination"
    txt <- "- Importation"
  }
  
  #------------------
  #    Analysis
  #------------------
  
  # Country as destination
  matching_vector <- str_detect(data[,way], country)
  
  # list of the categories (among the line that have "Country" as origin)
  # -> Products (categories) exporting by the country 
  country_cat <- data[matching_vector,"category"] 
  
  # Handling of this categories
  # Regular expression for spliting the categories
  regex <- "/(.*)/(.*)/(.*)"
  cat <- str_match(country_cat, regex)
  
  # Counting this categories 
  tab <- table(cat[,3])   #cat[,3] : 2nd category 
  tab <- sort(tab, decreasing = TRUE)  # Sorting (biggest in first) 
  tab <- tab[1:10] # Taking only the most important
  
  #-----------------
  #    Pie Chart     
  #-----------------
  
  # 1- Labels :
  # Calculation in percentage
  piepercent<- round(100*tab/sum(tab), 1)
     # round(a,1) : one digit after the comma
  
  lab <- c()
  
  for(i in 1:length(piepercent)) {
    lab[i] <- paste(piepercent[[i]], "%", sep=" ")
  }
  
  # 2- Title :
  title <- paste(country, txt, sep=" ")
  
  # 3- Colors :
  c <- rainbow(length(piepercent))
 
  # 4- Plot :
  pie3D(piepercent,labels = lab,labelcex = 1, main = title ,col=c, theta = 0.9, explode = 0.04)
  
  # 5- Legend :
  legend(x=-2.3,y=-1.1,names(piepercent), cex = 0.8, fill = c,ncol=4,border=NA, xpd=NA)
  
  # Frame
  box(which = "inner", lty = "solid")
}

country_Export()
```

We can notice that most of exportations are drugs. That is not surprising since drugs are the products the most sold. This pie chart show that there is a lot of variety in market. Althought, a huge part concerns "Cannabis & Hashish". We can also notice that Psychedelics and other highly dangerous drugs are significantly present.

We took the example of United Kingdom but most of European countries follow the same rules.

6. Let's have a look at the exportations of China which are of a different kind than United Kingdom :


```{r Exportation China}
#-----------------------------------------------
#   Importation / Exportation of a country
#-----------------------------------------------

country_Export <- function() {

  #-------------------
  #  Initialization
  #-------------------

  country <- "China"
  num <- 0
  
  # Importation / Exportation :
  if (num == 0) { 
    way <- "origin"
    txt <- "- Exportation"
  } else if (num == 1) {
    way <- "destination"
    txt <- "- Importation"
  }
  
  #------------------
  #    Analysis
  #------------------
  
  # Country as destination
  matching_vector <- str_detect(data[,way], country)
  
  # list of the categories (among the line that have "Country" as origin)
  # -> Products (categories) exporting by the country 
  country_cat <- data[matching_vector,"category"] 
  
  # Handling of this categories
  # Regular expression for spliting the categories
  regex <- "/(.*)/(.*)/(.*)"
  cat <- str_match(country_cat, regex)
  
  # Counting this categories 
  tab <- table(cat[,3])   #cat[,3] : 2nd category 
  tab <- sort(tab, decreasing = TRUE)  # Sorting (biggest in first) 
  tab <- tab[1:10] # Taking only the most important
  
  #-----------------
  #    Pie Chart     
  #-----------------
  
  # 1- Labels :
  # Calculation in percentage
  piepercent<- round(100*tab/sum(tab), 1)
     # round(a,1) : one digit after the comma
  
  lab <- c()
  
  for(i in 1:length(piepercent)) {
    lab[i] <- paste(piepercent[[i]], "%", sep=" ")
  }
  
  # 2- Title :
  title <- paste(country, txt, sep=" ")
  
  # 3- Colors :
  c <- rainbow(length(piepercent))
 
  # 4- Plot :
  pie3D(piepercent,labels = lab,labelcex = 1, main = title ,col=c, theta = 0.9, explode = 0.04)
  
  # 5- Legend :
  legend(x=-2.3,y=-1.1,names(piepercent), cex = 0.8, fill = c,ncol=4,border=NA, xpd=NA)

  # Frame
  box(which = "inner", lty = "solid")
  
}

country_Export()
```

What is suprising is that, unlike most of countries, China exports more Jewelry than Drugs. Although, drugs are still widely presents. Moreover, we can notice that the category electronics appears.

7. Let's compare France exportations with France importations and see if there is a difference between them.



```{r Export / Import FR}
  #-----------------------------------------------
  #   Importation / Exportation of a country
  #-----------------------------------------------
  
Country_Export_Import <- function() {

    #-------------------
    #  Initialization
    #-------------------
    
    country <- "France"
    
    #---------------------------
    #    Analysis - Exportation
    #---------------------------
    
    # Country as origin
    matching_vector <- str_detect(data[,"origin"], country)
    
    # list of the categories (among the line that have "Country" as origin)
    # -> Products (categories) exporting by the country 
    country_cat <- data[matching_vector,"category"] 
    
    # Handling of this categories
    # Regular expression for spliting the categories
    regex <- "/(.*)/(.*)/(.*)"
    cat <- str_match(country_cat, regex)
    
    # Counting this categories 
    tab_exp <- table(cat[,3])   #cat[,3] : 2nd category 
    tab_exp <- sort(tab_exp, decreasing = TRUE)  # Sorting (biggest in first) 
    tab_exp <- tab_exp[1:10] # Taking only the most important
    
    #---------------------------
    #    Analysis - Importation
    #---------------------------
    
    # Country as destination
    matching_vector <- str_detect(data[,"destination"], country)
    
    # list of the categories (among the line that have "Country" as destination)
    # -> Products (categories) importing by the country 
    country_cat <- data[matching_vector,"category"] 
    
    # Handling of this categories
    # Regular expression for spliting the categories
    regex <- "/(.*)/(.*)/(.*)"
    cat <- str_match(country_cat, regex)
    
    # Counting this categories 
    tab_imp <- table(cat[,3])   #cat[,3] : 2nd category 
    tab_imp <- sort(tab_imp, decreasing = TRUE)  # Sorting (biggest in first) 
    tab_imp <- tab_imp[1:10] # Taking only the most important
    
    #-------------------------
    #    Analysis - Fusion
    #-------------------------
    
    # Transformation in data frame
    tab_exp <- as.data.frame(tab_exp)
    tab_imp <- as.data.frame(tab_imp)
    
    # Merger of the 2 data frame in order to have the same labels 
    tab <- merge(tab_exp,tab_imp,by.x="Var1",by.y="Var1",all = TRUE)
    
    # Handling of the "NA" value (substitution by 0)
    for (j in 2:3) {
      for(i in 1:length(tab[,j])){
        if(is.na(tab[i,j])) {tab[i,j] <-0}
      }
    }  
    
    #---------------------------
    #    Pie Chart - Exporation     
    #---------------------------
    
    # ploting 2 graphics om the same picture
    par(mfrow = c(1,2))
    
    # 1- Labels :
    # Calculation in percentage
    piepercent <- round(100*tab[,2]/sum(tab[,2]), 1)
    # round(a,1) : one digit after the comma
    
    lab <- c()
    
    for(i in 1:length(piepercent)) {
      if(piepercent[[i]] == 0) {lab[i] <- ""} 
      else {lab[i] <- paste(piepercent[[i]], "%", sep=" ")}
    }

    # 2- Colors :
    c <- rainbow(length(tab[,1]))
    
    # 3- Plot :
    pie(piepercent,labels=lab,col=c)
    mtext("Exportation",cex=1)
    
    #----------------------------
    #    Pie Chart - Importation     
    #----------------------------
    
    # 1- Labels :
    # Calculation in percentage
    piepercent <- round(100*tab[,3]/sum(tab[,3]), 1)
    # round(a,1) : one digit after the comma
    
    lab <- c()
    
    for(i in 1:length(piepercent)) {
      if(piepercent[[i]] == 0) {lab[i] <- ""}
      else {lab[i] <- paste(piepercent[[i]], "%", sep=" ")}
    }

    # 2- Plot :
    pie(piepercent, labels=lab, col=c)
    mtext("Importation",cex=1)
    
    #------------------
    #   General - Plot     
    #-----------------
    
    par(oma=c(0,0,1.8,0))
    title("France",outer=TRUE)
    legend(x=-4,y=-1,tab[,1], cex = 0.8, fill=c,ncol=3,border=NA, xpd=NA)
    
    # Frame
    box(which = "outer", lty = "solid")
    
}

Country_Export_Import()
    
```

It is noticeable that both are different. The part of each category is different and some of them doesn't appear systematicaly in the other pie chart. But we have to moderate our conclusions since most of the value given by the importation variable doesn't target a unique country and we were compelled to ad "Europe" values to our model.

8. We wondered if products sold in AlphaBay are cheapest than what offer street sellers. Firstly, we calculated the average price in AlphaBay of the most common drugs. We obtain the result below.  



```{r Drugs Prices}

DrugsPrices <- function() {
  
  drugs <- c("Cocaine", "Meth", "Opioids", "Cannabis", "Steroids", "Ecstasy", "Ketamine", "Heroin",  "NBOME","Shrooms", "Tobacco", "Benzos", "Paraphernalia")
  
  med <-c()
  for(i in 1:length(drugs)){
    matching_vector <- selectDrug(drugName =  drugs[i]);
    med[i] <- median((data[matching_vector, "priceUnitDose"]))
  }
  priceDrugs <- data.frame(drugs, med); 
  
  priceDrugs$med <- round(priceDrugs$med,2)
  
  priceDrugs <- priceDrugs[order(priceDrugs$med, decreasing=TRUE), ]
  
  par(las=1) # Display yaxis horizontally
  par(mar=c(4,8,3,2)) # Give space for yaxis
  
  barp <- barplot(priceDrugs$med, main="Average Price of Drugs in the World", names.arg = priceDrugs$drugs, xlim = c(0,max(priceDrugs$med+100)), cex.names = 0.8, col =rainbow(length(priceDrugs$drugs)), horiz =TRUE)
  barp <- text(y = barp, x = priceDrugs$med, label = paste(priceDrugs$med, " $", sep=""), pos=4 , cex = 0.8, col= "Black")
  
  # Frame
  box(which = "outer", lty = "solid")
  
  return (priceDrugs)

}

priceDrugs <- DrugsPrices()
```
9. Finally, we were looking to some information  about the price of street sellers for same drugs as above. Thus, we gathered these information in articles and websites. Unfortunately, we failed to obtain information on some drugs. Below is the result of we found.

```{r Comparison articles & data, message=FALSE, warning=FALSE}

#-----------------------------------------
#   Prices find on articles
#-----------------------------------------

DrugsPricesDoc <- function(){
  
  cols <- c("Cocaine", "Meth", "Opioids",      "Cannabis"      , "Steroids", "Ecstasy", "Ketamine", "Heroin",  "NBOME","Shrooms", "Tobacco", "Benzos", "Paraphernalia" , "MDMA", "Amphetamine", "Crack", "LSD"   , "URL")

  ref1  <- c(    35   ,   200  ,     NA   ,     (5.3 + 7.85)/2   ,    NA     ,     15   ,     25    ,    100   ,     NA  ,    NA   ,    NA    ,     NA  ,        NA      ,    40 ,   5         ,  NA    ,  NA     ,   "http://www.drugwise.org.uk/how-much-do-drugs-cost/")
  ref2  <- c(    67   ,   NA   ,     NA   ,      51              ,    NA     ,     15   ,     32    ,    129   ,     NA  ,    NA   ,    NA    ,     NA  ,        NA      ,   51  ,   15        ,  97    ,  NA     , "http://www.telegraph.co.uk/news/uknews/crime/11346133/The-cost-of-street-drugs-in-Britain.html")
  ref3  <- c(    110  ,   80   ,     NA   ,      NA              ,    NA     ,     NA   ,     NA    ,    170   ,     NA  ,    5.7  ,    NA    ,     NA  ,        NA      ,  150  ,   NA        ,   NA   ,  12000  ,   "http://www.rehabcenter.net/the-average-cost-of-illegal-drugs-on-the-street/ " )
  ref4  <- c(    80   ,   109  ,     NA   ,      NA              ,    NA     ,   19.12  ,     NA    ,    91.16 ,     NA  ,    NA   ,    NA    ,     NA  ,        NA      ,    NA ,   NA        ,   NA   ,     NA  ,   " http://o.canada.com/business/interactive-what-illegal-drugs-cost-on-the-street-around-the-world")
  ref5  <- c(     64  ,   NA   ,     NA   ,      NA              ,    NA     ,     20   ,     NA    ,    NA    ,     NA  ,    NA   ,    NA    ,     NA  ,        NA      ,    NA ,   NA        ,  NA    ,   NA    , " http://www.thestudentpocketguide.com/2012/01/student-life/health-and-relationships/facts-about-drugs/")
  
  doc_drugs <- t(data.frame(ref1, ref2, ref3, ref4, ref5))
  colnames(doc_drugs) <- cols
  
  # Calculate the mean price of each drugs find on articles
  price_doc <- c()
  for(i in 1 : length(cols)){
    price_doc[i] <- summary(as.numeric(doc_drugs[,i]))[[4]]
  }
  price_doc.data <- data.frame(cols, price_doc)
  
  
  # Merge the previous dataframe which correspond to the mean price of each drugs in the data
  # with the dataframe created above
  beside_plot <- merge(price_doc.data, priceDrugs, by.x ="cols", by.y ="drugs") 
  
  rownames(beside_plot) <- beside_plot[,1]
  beside_plot <- beside_plot[,-1]
  
  # Creating the barplot
  par(las=1)#display yaxis horizontally
  par(mar=c(6,8,4,3)) # Give space for yaxis
 
  b <- barplot(rbind(beside_plot[,1], beside_plot[,2]), main="Average price of Drugs", xlim = c(0, 400),
          xlab="Price of Drugs", beside=TRUE, names.arg = rownames(beside_plot), col=1:2, horiz = TRUE, space = c(0,0.4), cex.names = 0.8)
  
  axis(side=1,at=c(50,150,250,350),labels=c(50,150,250,350))
  
  
  lab <- c("Street", "AlphaBay")
  
  legend("topright",lab,fill=1:2, cex=0.8)
  
  # Frame
  box(which = "outer", lty = "solid")
}

DrugsPricesDoc()

```

Globally we can notice that price of the street sellers are often largely higher than AlphaBay ads. In few cases both prices tend to be similar.

# - Data mining
***
Secondly, we have performed some data minig techniques in order to discover hidden rule and correlation in the database and also to predict the value of one variable given other values.

## - Decision tree

```{r DTsellers}
#----------------------------------------------------------------------
#                  Decision tree - CART algorithm
#   Prediction of the seller knowing the price / category / origin
#                               Plot
#-----------------------------------------------------------------------

Dtsellers <- function(){  

  #-----------------
  #   New Data 
  #-----------------
  
  # Select all "Drugs & Chemicals" ads
  matching_vector <- c( str_detect(data$category, "Drugs & Chemicals"))
  dectree.data <- data[matching_vector,]
  
  # Select the column of the data that are interesting for the tree
  # ie removing colunm like "id" or "url" that don't give any informations
  dectree.data <- subset(dectree.data, select=c(origin,category,seller,priceUnitDose))
  # Subset : choose the colunm that you want
  
  # Handling : column categorie
  # Regular expression for spliting the categories
  regex <- "/(.*)/(.*)/(.*)"
  cat <- str_match(dectree.data$category, regex)
  dectree.data$category <- cat[,3] # keep only the second part
  
  # Handling : seller
  tab_sel <- table(dectree.data$seller)
  tab_sel <- sort(tab_sel, decreasing=TRUE)  # Sorting (biggest in first)
  tab_sel <- tab_sel[1:5] # Taking only the most important : main sellers
  name_sel <- names(tab_sel)
  # New data keeping only the main sellers
  dectree.data <-subset(dectree.data, seller %in% name_sel) 
  
  # Random rows :
  dectree.data <- dectree.data[sample(nrow(dectree.data),nrow(dectree.data),replace=FALSE), ]
  
  #---------------------
  #   Decision tree
  #---------------------
  
  # Factor
  dectree.data$seller <- factor(dectree.data$seller)
  
  # Half of the data for making the decision tree
  train.data <- dectree.data[1:(floor(nrow(dectree.data))/2),]
  
  # Creation of the tree
  tree <- rpart(seller ~.,data=train.data, method="class") 
  
  # Plot
  fancyRpartPlot(tree)

  # Frame
  box(which = "outer", lty = "solid")
  
  #--------------------
  #   Prediction
  #--------------------
  
  # The other half for the prediction
  pred.data <- dectree.data[(floor(nrow(dectree.data)/2)+1):nrow(dectree.data),]
  
  # Making prediction
  pred <- predict(tree,pred.data,type="class")
  
  # Analysis:
  
    # Comparison between the result and the prediction (prediction in colunm)
    conf <- table(pred.data[,match("seller",names(pred.data))],pred)
    
    # Accurency
    acc <- sum(diag(conf)) / sum(conf)
    
  
  print(conf)
  sprintf("The accurency is : %.2f %%", acc*100)
 
}

Dtsellers()

```

```{r}
#----------------------------------------------------------------------
#                  Decision tree - CART algorithm
#   Prediction of the seller knowing the price / category / origin
#                              Results
#-----------------------------------------------------------------------

Dtsellers2 <- function(){  

  #-----------------
  #   New Data 
  #-----------------
  
  # Select all "Drugs & Chemicals" ads
  matching_vector <- c( str_detect(data$category, "Drugs & Chemicals"))
  dectree.data <- data[matching_vector,]
  
  # Select the column of the data that are interesting for the tree
  # ie removing colunm like "id" or "url" that don't give any informations
  dectree.data <- subset(dectree.data, select=c(origin,category,seller,priceUnitDose))
  # Subset : choose the colunm that you want
  
  # Handling : column categorie
  # Regular expression for spliting the categories
  regex <- "/(.*)/(.*)/(.*)"
  cat <- str_match(dectree.data$category, regex)
  dectree.data$category <- cat[,3] # keep only the second part
  
  # Handling : seller
  tab_sel <- table(dectree.data$seller)
  tab_sel <- sort(tab_sel, decreasing=TRUE)  # Sorting (biggest in first)
  tab_sel <- tab_sel[1:10] # Taking only the most important : main sellers
  name_sel <- names(tab_sel)
  # New data keeping only the main sellers
  dectree.data <-subset(dectree.data, seller %in% name_sel) 
  
  # Random rows :
  dectree.data <- dectree.data[sample(nrow(dectree.data),nrow(dectree.data),replace=FALSE), ]
  
  #---------------------
  #   Decision tree
  #---------------------
  
  # Factor
  dectree.data$seller <- factor(dectree.data$seller)
  
  # Half of the data for making the decision tree
  train.data <- dectree.data[1:(floor(nrow(dectree.data))/2),]
  
  # Creation of the tree
  tree <- rpart(seller ~.,data=train.data, method="class") 

  #--------------------
  #   Prediction
  #--------------------
  
  # The other half for the prediction
  pred.data <- dectree.data[(floor(nrow(dectree.data)/2)+1):nrow(dectree.data),]
  
  # Making prediction
  pred <- predict(tree,pred.data,type="class")
  
  # Analysis:
  
    # Comparison between the result and the prediction (prediction in colunm)
    conf <- table(pred.data[,match("seller",names(pred.data))],pred)
    
    # Accurency
    acc <- sum(diag(conf)) / sum(conf)
  
  print(conf)
  sprintf("The accurency is : %.2f %%", acc*100)
}

Dtsellers2()
```



## - Association rule

We have wondered if there are links between some drugs. That is to say, if this is possible to cluster some drugs.
To do so, firstly, we have created a new data frame with by rows sellers and by columns different sub-categories of "Drugs & Chemicals". In each cell, value is True or False if the dealer has already sold something in this sub-category.
Then we have applied Apriori algorithm. We fixed one drug, that must be in the itemset. Here it is Ecstasy. The result can be seen below.

```{r Ass Rules Sellers-Category}

#--------------------------------------------------------
#       Association Rules - Apriori algorithm     
#     Guess if this dealer is selling this drugs
#--------------------------------------------------------

AssRSellersCat <- function(){
  
  #------------------------------
  #  New Data frame for analysis
  #------------------------------
  
  # Select all ads of "Drugs & Chemicals"
  matching_vector <- c( str_detect(data$category, "Drugs & Chemicals"))
  data_drugs <- data[matching_vector, ]
  
  # Handling of this categories
  # Regular expression for spliting the categories
  regex <- "/(.*)/(.*)/(.*)"
  cat_exp <- str_match(data_drugs$category, regex)
  data_drugs$category <- cat_exp[,3]
  
  # Get rid of category "Other"
  matching_vector <- !c( str_detect(data_drugs$category, "Other"))
  data_drugs <- data_drugs[matching_vector, ]
  
  # List all the sellers
  sellers <-sort(table(data_drugs$seller), decreasing = TRUE)
  sellers <- sellers[ sellers != "Null"]
  sellers <- sellers [1:100]
  
  #List all categories concerning drugs
  list_category <- table(data_drugs[,"category"])
  list_cat_drugs <- list_category [ list_category != 0]
  
# Step 1 : initialise a data.frame with the information of the first seller
  
  # Select all categories of the seller  
  matching_vector <- c( str_detect(data$seller, names(sellers)[1]))
  cat_seller <-summary(data.frame(data[matching_vector, "category"]))
  
  # Loop which creates a boolean vector which tells if the seller sells stuffs in each category 
  bool_cat <-c()
  bool_vec <-c()
  for( i in 1: length(list_cat_drugs)){
    bool_vec <- str_detect(cat_seller, names(list_cat_drugs)[i])
    
    bool <- FALSE 
    for(j in 1:length(bool_vec)){
      bool <- bool || bool_vec[j]
    }
    bool_cat[i] <- bool
    
  }
  
  cat_seller.data <- t(data.frame(bool_cat))
  colnames(cat_seller.data) <- names(list_cat_drugs)
  
#Step 2 : Do the same for the other sellers
  
  for(k in 2 : length(sellers)){
    # Select all categories of the seller  
    matching_vector <- c( str_detect(data$seller, names(sellers)[k]))
    cat_seller <-summary(data.frame(data[matching_vector, "category"]))
    
    # Loop which creates a boolean vector which tells if the seller sells stuffs in each category 
    bool_cat <-c()
    bool_vec <-c()
    for( i in 1: length(list_cat_drugs)){
      bool_vec <- str_detect(cat_seller, names(list_cat_drugs)[i])
      
      bool <- FALSE 
      for(j in 1:length(bool_vec)){
        bool <- bool || bool_vec[j]
      }
      bool_cat[i] <- bool
      
    }
    
    cat_seller.data <- rbind(cat_seller.data,bool_cat)
    
  }
  
  rownames(cat_seller.data)<- names(sellers)

  #-------------------------
  #      Ass Rules
  #-------------------------
  
  # Association Rules with rhs containing "Ecstasy" only
  rules <- apriori(cat_seller.data,
                   parameter = list(minlen=2, supp=0.05, conf=0.8),
                   appearance = list(rhs=c("Ecstasy"),default="lhs"),
                   control = list(verbose=F))
  
  rules.sorted <- sort(rules, by="lift")
  inspect(rules.sorted, linebreak = TRUE)
  
  # Plot graph of rules
  plot(rules.sorted[1:5], method="graph", control=list(type="items"),main ="")
  mtext("Association Rules on the product range of sellers" , cex = 1.2)
  
  # Frame
  box(which = "outer", lty = "solid")

}

AssRSellersCat()

```

The algorithm succeeds to find some rules in the data frame that means that some drugs can effectively be clustered. The support is between 5% and 15% so it is frequent to have these itemsets. Moreover the confidence is above 80% that means that if we have the itemset on the left we are almost certain to have the drug on the right. 
We can interpret from these rules that sellers often deal more than one product. And these products can be clustered. 

```{r Ass Rules Origin}
#--------------------------------------------------------
#       Association Rules - Apriori algorithm     
#     Guess if United States is the origin of the ad
#--------------------------------------------------------

AssROriginSellerCat <- function(){  
  #------------------------------
  #  New Data frame for analysis
  #------------------------------

  # Select all ads of "Drugs & Chemicals"
  matching_vector <- c( str_detect(data$category, "Drugs & Chemicals"))
  data_drugs <- data[matching_vector, ]
  
  # Select some columns
  asso.data <- subset(data_drugs, select = c(origin,category))
  
  # Get rid of the first part of the category name "/Drugs & Chemicals/"
  asso.data$category <- gsub(pattern = "/Drugs & Chemicals/", replacement = "", asso.data$category)
  
  asso.data$origin <- factor(asso.data$origin)
  asso.data$category <-factor(asso.data$category)
  # asso.data$seller <- factor(asso.data$seller)
  
  # Association Rules with rhs containing one given country only
  rules <- apriori(asso.data,
                   parameter = list(minlen=2, supp=0.002, conf=0.5),
                   appearance = list(rhs=c("origin=United States"),default="lhs"),
                   control = list(verbose=F))
  
  rules.sorted <- sort(rules, by="lift")
  inspect(rules.sorted, linebreak = TRUE)
  
  # Plot graph of rules
  plot(rules.sorted, method="graph", control=list(type="items"),main ="")
  mtext("Association Rules on the category and seller to deduce the country" , cex = 1.2)
  
  # Frame
  box(which = "outer", lty = "solid")

}

AssROriginSellerCat()

```



```{r Bayesian Sellers}
#----------------------------------------------------------------------------------
#                       Bayesian Classification - Naive
#   Prediction of the Seller knowing the origin / price / category / products_sold
#-----------------------------------------------------------------------------------

BayesSellers <- function(){
  #-----------------
  #   New Data 
  #-----------------
  
  # Select all "Drugs & Chemicals" ads
  matching_vector <- c( str_detect(data$category, "Drugs & Chemicals"))
  bayesian.data <- data[matching_vector,]
  
  # Select the column of the data that are interesting
  # ie removing colunm like "id" or "url" that don't give any informations
  bayesian.data <- subset(bayesian.data, select=c(origin,category,seller,priceUnitDose, products_sold, sold_since ))
  # Subset : choose the colunm that you want
  
  # Handling : column category
  # Regular expression for spliting the categories
  regex <- "/(.*)/(.*)/(.*)"
  cat <- str_match(bayesian.data$category, regex)
  bayesian.data$category <- cat[,3] # keep only the second part
  
  sellers <- names(sort(table(bayesian.data$seller), decreasing = TRUE))[1:10]
  
  bayesian.data <-subset(bayesian.data, seller %in% sellers)
  
  bayesian.data$seller <- factor(bayesian.data$seller, labels = sellers)

  #---------------------
  #   Bayesian stat
  #---------------------
  
  # Random rows :
  bayesian.data <- bayesian.data[sample(nrow(bayesian.data),nrow(bayesian.data),replace=FALSE), ]
  
  train.data <- bayesian.data[1:floor(nrow(bayesian.data)/2),]
  pred.data <- bayesian.data[(floor(nrow(bayesian.data)/2)+1):nrow(bayesian.data),]
  
  model <- naiveBayes(seller ~ ., data =  train.data)
  
  
  preds <- predict(model, newdata = pred.data)
  conf_matrix <- table(preds, pred.data$seller)
  acc <- sum(diag(conf_matrix)) / sum(conf_matrix)
  
  print(conf_matrix)
  sprintf("The accurency is : %.2f %%", acc*100)
}

BayesSellers()

```

# - References
***
